### 2024-11-10 README.Rmd
revise README

```{r, eval=FALSE}
sbert_embeddings <- function(texts) {
	text::textEmbed(
	  texts,
	  model = "sentence-transformers/all-MiniLM-L12-v2", # model name
	  layers = -2,  # second to last layer (default)
	  tokens_select = "[CLS]", # use only [CLS] token
	  dim_name = FALSE,
	  keep_token_embeddings = FALSE
  )$texts[[1]]
}

@@

```{r}
library(quanteda)

valence_corp <- corpus(valence_df, docid_field = "id")
valence_corp

valence_dfm <- valence_corp |> 
	tokens() |> 
	dfm()

valence_embeddings_df <- valence_dfm |> 
	textstat_embedding(glove_twitter_25d)
valence_embeddings_df
```

@@

@@

>>>>

```{r, eval=FALSE}
# function that takes character vector and outputs data frame
sbert_embeddings <- function(texts) {
	text::textEmbed(
	  texts,
	  model = "sentence-transformers/all-MiniLM-L12-v2", # model name
	  layers = -2,  # second to last layer (default)
	  tokens_select = "[CLS]", # use only [CLS] token
	  dim_name = FALSE,
	  keep_token_embeddings = FALSE
  )$texts[[1]]
}

@@

```{r, warning=FALSE, message=FALSE}
library(quanteda)

# corpus
valence_corp <- corpus(valence_df, docid_field = "id")
valence_corp

# dfm
valence_dfm <- valence_corp |> 
	tokens() |> 
	dfm()

# compute embeddings
valence_embeddings_df <- valence_dfm |> 
	textstat_embedding(glove_twitter_25d)
valence_embeddings_df
```

@@

`normalize()` and `normalize_rows()` scale embeddings such that their magnitude is 1, while their angle from the origin is unchanged.

@@

The magnitude, norm, or length of a vector is its Euclidean distance from the origin.
